---
title: "Alcohol vs Seat choice"
author: "Jaelynn Schultz"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
As indicated by the plot, the median and first and third percentiles for the back seat box plot are  
much higher when compared to the front and middle seats (this is including the maximum). The front  
seat data appears to have the lowest median and maximum, and the middle had the greatest number of  
outliers. The people in the back consume more alcohol than those in the middle or back seats.  
    
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
Based on the data, majority of the people are seated in the middle seats, however, the back seats  
show the greatest median, max, first and third quartile, and mean. This indicates that those in  
the back show higher levels of alcohol consumption. 
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
  
The low p-value indicates that there is an issue in the data, and it further indicates that  
more statistical testing should be done through a TukeyHSD test.

```{r}
plot(TukeyHSD(model1))
```
  
From this data we can see that the alcohol consumption of the front and the middle are not different, but the alcohol consumption of the front is less than the back and the same can be said of the middle and the back. Overall, the back shows more alcohol consumption than those in the middle or the front.  
  
## Conclusions

Based on the boxplots, numerical data, and the TukeyHSD, we can say with a high degree of certainty that those who sit in the back seats consume considerably more alcohol than those who sit in the middle or front rows, as there is a significant difference between the middle and back rows and the front and back rows, but not so much difference between the middle and front rows. 
  