---
title: "Alcohol vs Seat choice"
author: "Jaelynn Schultz"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot



```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
As indicated by the plot, the median and first and third percentiles for the back seat box plot are  
much higher when compared to the front and middle seats (this is including the maximum). The front  
seat data appears to have the lowest median and maximum, and the middle had the greatest number of  
outliers. The people in the back consume more alcohol than those in the middle or back seats.  
    
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
  
Based on the data, majority of the people are seated in the middle seats, however, the back seats  
show the greatest median, max, first and third quartile, and mean. This indicates that those in  
the back show higher levels of alcohol consumption. 
  
## Inferential Tests

## Conclusions


